---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# CrossClustering

[![Travis Build Status](https://travis-ci.com/CorradoLanera/CrossClustering.svg?branch=develop)](https://travis-ci.com/CorradoLanera/CrossClustering)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/CorradoLanera/CrossClustering?branch=develop&svg=true)](https://ci.appveyor.com/project/CorradoLanera/CrossClustering)
<!-- [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/CrossClustering)](http://cran.r-project.org/package=CrossClustering) -->
[![Coverage Status](https://codecov.io/gh/CorradoLanera/CrossClustering/branch/develop/graph/badge.svg)](https://codecov.io/gh/CorradoLanera/CrossClustering?branch=develop)

CrossClustering is a partial clustering algorithm that combines the Ward's
minimum variance and Complete Linkage algorithms, providing automatic
estimation of a suitable number of clusters and identification of outlier
elements.

## Example

This is a basic example which shows you how to the main function, i.e. `CrossClustering()` works:

```{r example}
## basic example code
library(CrossClustering)

#### method = "complete"
data(toy)

### toy is transposed as we want to cluster samples (columns of the original
### matrix)
d <- dist(t(toy), method = "euclidean")

### Run CrossClustering
toyres <- CrossClustering(d, k.w.min = 2, k.w.max = 5, k2.max = 6,
out = TRUE)
toyres
```

Another useful function worth to mention is `PermSignificanceARI`:
```{r}
CC_clusters <- which_cluster(toyres$Cluster.list, toyres$n.total)
PermSignificanceARI(
  ground_truth = c(1, 1, 2, 2, 3, 3, 4),
  partition    = CC_clusters
)
```


## Install
CrossClustering package is on CRAN, use the standard method to install it.
`install.packages('CrossClustering')`

## Feature request
If you need some more features, please write to Paola Tellaroli
<paola.tellaroli@unipd.it>



## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example) to
Paola Tellaroli K<paola.tellaroli@unipd.it>

