---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig_path = "README-"
)
```

# CrossClustering

[![Travis Build Status](https://travis-ci.org/CorradoLanera/CrossClustering.svg?branch=develop)](https://travis-ci.org/CorradoLanera/CrossClustering)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/CorradoLanera/CrossClustering?branch=develop&svg=true)](https://ci.appveyor.com/project/CorradoLanera/CrossClustering)
[![CRAN Status Badge](http://www.r-pkg.org/badges/version/CrossClustering)](https://cran.r-project.org/web/packages/CrossClustering)
[![Coverage Status](https://codecov.io/gh/CorradoLanera/CrossClustering/branch/develop/graph/badge.svg)](https://codecov.io/gh/CorradoLanera/CrossClustering?branch=develop)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)

CrossClustering is a partial clustering algorithm that combines the Ward's
minimum variance and Complete Linkage algorithms, providing automatic
estimation of a suitable number of clusters and identification of outlier
elements.

## Example

This is a basic example which shows you how to the main function, i.e. 
`cc_crossclustering()` works:

```{r example}
## basic example code
library(CrossClustering)

#### method = "complete"
data(toy)

### toy is transposed as we want to cluster samples (columns of the original
### matrix)
d <- dist(t(toy), method = "euclidean")

### Run CrossClustering
toyres <- cc_crossclustering(d, k_w_min = 2, k_w_max = 5, k2_max = 6,
out = TRUE)
toyres
```

Another useful function worth to mention is `ari`:
```{r}
clusters <- iris[-5] %>%
 dist() %>%
 hclust(method = 'ward.D') %>%
 cutree(k = 3)

ground_truth <- iris[[5]] %>%
  as.numeric()

table(ground_truth, clusters) %>% 
  ari()
```


## Install
### CRAN version
CrossClustering package is on CRAN, use the standard method to install it.
`install_packages('CrossClustering')`

### develop version
To install the develop branch of CrossClastering package, use:
```{r eval=FALSE}
# install.packages(devtools)
devtools::install_github('CorradoLanera/CrossClustering', ref = 'develop')
```


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example) to
<https://github.com/CorradoLanera/CrossClustering/issues>


## References

**Tellaroli P, Bazzi M., Donato M., Brazzale A. R., Draghici S. (2016).
Cross-Clustering: A Partial Clustering Algorithm with Automatic
Estimation of the Number of Clusters. PLoS ONE 11(3):   e0152333.
<https://doi.org/10.1371/journal.pone.0152333>**

**Tellaroli P, Bazzi M., Donato M., Brazzale A. R., Draghici S. (2017).
E1829: Cross-Clustering: A Partial Clustering Algorithm with Automatic
Estimation of the Number of Clusters. CMStatistics 2017, London 16-18
December, Book of Abstracts (ISBN 978-9963-2227-4-2)**


