---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# CrossClustering

CrossClustering is a partial clustering algorithm that combines the Ward's
minimum variance and Complete Linkage algorithms, providing automatic estimation
of a suitable number of clusters and identification of outlier elements.

## Example

This is a basic example which shows you how to the main function, i.e. `CrossClustering()` works:

```{r example}
## basic example code
library(CrossClustering)

#### method = "complete"
### Generate simulated data
toy <- matrix(NA, nrow = 10, ncol = 7)
colnames(toy) <- paste("Sample", 1:ncol(toy), sep = "")
rownames(toy) <- paste("Gene"  , 1:nrow(toy), sep = "")
set.seed(123)

toy[, 1:2] <- rnorm(n = nrow(toy) * 2, mean = 10, sd  = 0.1)
toy[, 3:4] <- rnorm(n = nrow(toy) * 2, mean = 20, sd  = 0.1)
toy[, 5:6] <- rnorm(n = nrow(toy) * 2, mean = 5 , sd  = 0.1)
toy[,   7] <- runif(n = nrow(toy)    , min  = 0 , max = 1  )

### toy is transposed as we want to cluster samples (columns of the original
### matrix)
d <- dist(t(toy), method = "euclidean")

### Run CrossClustering
toyres <- CrossClustering(d, k.w.min = 2, k.w.max = 5, k2.max = 6,
out = TRUE)
toyres
```

Another useful function worth to mention is `PermSignificanceARI`:
```{r}
CC_clusters <- sapply(seq_len(ncol(toy)),
 which_cluster,
 toyres$Cluster.list
)
PermSignificanceARI(
  ground_truth = c(1, 1, 2, 2, 3, 3, 4),
  partition    = CC_clusters
)
```


## Install
CrossClustering package is on CRAN, use the standard method to install it.
`install.packages('CrossClustering')`

## Feature request
If you need some more features, please write to Paola Tellaroli
<paola.tellaroli@unipd.it>



## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example) to
Paola Tellaroli K<paola.tellaroli@unipd.it>

